Automatic Visual Inference for Linear Regression

### 2022-03-16 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
add inc slide

.pull-left-center[
```{r plot1}
library(visage)

@@

#### This is a residual plot of a simple linear regression.

@@

#### However, the residuals are actually simulated from a **correctly specified model**!

@@

@@

#### To train computer vision models, we use simulation data generated from two linear regression model with **non-linearity** and **heteroskedasticity** issues.

@@

#### In the simulation, $X_i$, $i=1,...,n$, has equal chance to follow one of the following distributions: $N(0, 0.09)$, $U(-1, 1)$, $Lognormal(0,0.36)/3 - 1$ and $-Lognormal(0,0.36)/3 + 1$. These distributions are chosen such that most the realizations will fall between $-1$ and $1$.

#### The distribution of $Z_i$, $i=1,...,n$, has $50$% chance to be a uniform distribution ranged from $-1$ to $1$, and $50$% chance to be a discrete uniform distribution with $z_n$ outcomes simulated from a uniform distribution ranged from $-1$ to $1$. $z_n$ itself is a discrete uniform distribution with outcomes $\{x: 9<x<21 \text{ and } x \in \mathbb{Z} \}$, which defines the number of possible values $Z_i$ could take.

>>>>

.pull-left-center[
```{r}
library(visage)

@@

.pull-left-center[
```{r}
filter(eval_data, id == 9586, null == TRUE) %>%
  VI_MODEL$plot(theme = theme_light(base_size = 12), size = 1) +
  ylab("Residuals") +
  xlab("Fitted values")
# 68

@@

.pull-left-center[
```{r}
filter(eval_data, id == 9586, null == TRUE) %>%
  VI_MODEL$plot(theme = theme_light(base_size = 12), size = 1) +
  ylab("Residuals") +
  xlab("Fitted values")
# 68

#### However, the residuals are actually obtained from a **correctly specified classical normal linear model**!

.pull-left-center[
```{r}
filter(eval_data, id == 9586, null == TRUE) %>%
  VI_MODEL$plot(theme = theme_light(base_size = 12), size = 1) +
  ylab("Residuals") +
  xlab("Fitted values")
# 68

#### However, the residuals are actually obtained from a **correctly specified classical normal linear model**!

@@

.pull-right-center[
```{r}
VI_MODEL$plot_lineup(manual_lineup, 
                     theme = theme_light(),
                     remove_grid_line = TRUE,
                     size = 0.3
                     ) +
  xlab("Fitted values") +
  ylab("Residuals")
```

.pull-right-center[
```{r}
VI_MODEL$plot_lineup(manual_lineup, 
                     theme = theme_light(),
                     remove_grid_line = TRUE,
                     size = 0.3
                     ) +
  xlab("Fitted values") +
  ylab("Residuals")
```

@@

#### We simulated data from two linear regression model with **non-linearity** and **heteroskedasticity** issues

@@

.pull-left[
#### $X_i$, $i=1,...,n$ follows one of the four distributions:
- $N(0, 0.09)$
- $U(-1, 1)$
- $Lognormal(0,0.36)/3 - 1$
- $-Lognormal(0,0.36)/3 + 1$

#### Most the realizations will fall between $-1$ and $1$.
]

.pull-right[
#### $Z_i$, $i=1,...,n$ follows one of the two distributions:
- $U(-1, 1)$
- Discrete uniform distribution with $z_n$ outcomes ranged from $-1$ to $1$

#### $z_n$ is sampled from $\{z_n: 9<z_n<21 \text{ and } z_n \in \mathbb{Z} \}$.
]

<!-- #### The distribution of $Z_i$, $i=1,...,n$, has $50$% chance to be a uniform distribution ranged from $-1$ to $1$, and $50$% chance to be a discrete uniform distribution with $z_n$ outcomes simulated from a uniform distribution ranged from $-1$ to $1$. $z_n$ itself is a discrete uniform distribution with outcomes $\{x: 9<x<21 \text{ and } x \in \mathbb{Z} \}$, which defines the number of possible values $Z_i$ could take. -->
